Prefetching SPARQL query cacher

### 2016-05-19 dissertation/cache-proxy.tex
more on the use of roles

These query planners are a good example of the virtues of traits-based
programming: \pmodule{AtteanX::QueryPlanner::Cache} extends the basic query
planner of the Attean framework, \pmodule{Attean::QueryPlanner}, but
also composes the following roles:
\pmodule{Attean::API::NaiveJoinPlanner},
\pmodule{Attean::API::SimpleCostPlanner},
\pmodule{AtteanX::API::JoinRotatingPlanner},
\pmodule{AtteanX::Query::AccessPlan::SingleQuadBGP} and
\pmodule{AtteanX::Query::AccessPlan::Cache}.

\pmodule{Attean::QueryPlanner} has only minimal functionality,
everything else is provided by the roles. With conventional single
inheritance, one would end up with a rather complex base class. While
multiple inheritance or mix-in could be employed, \cite{traits}
explains why this is an inferior solution.

>>>>

These query planners are a good example of the virtues of traits-based
programming, as they are typically customised along different axes:
access plans, cost estimation, planning of joins within Basic Graph
Patterns or left joins, rewriting (like gathering quad patterns to
blocks), etc. In the case of our query planner that combines a remote
endpoint with a local cache, named
\pmodule{AtteanX::QueryPlanner::Cache}, the basic query planner of the
Attean framework, \pmodule{Attean::QueryPlanner} is extended
(i.e. inherited from), but also composes the following roles:
\pmodule{Attean::API::NaiveJoinPlanner},
\pmodule{Attean::API::SimpleCostPlanner},
\pmodule{AtteanX::API::JoinRotatingPlanner},
\pmodule{AtteanX::Query::AccessPlan::SingleQuadBGP} and
\pmodule{AtteanX::Query::AccessPlan::Cache}.

\pmodule{Attean::QueryPlanner} has only minimal functionality,
everything else is provided by the roles. Conventional single
inheritance is constrained to tree structure, and would result in a
very complex system. Another option is to use the factory method
pattern, where a factory object would need to be initialised to return
a suitable object for each axes of customisation.
